---
title: "R Notebook"
output: html_notebook
---


### Introduction

```{r setup}
knitr::opts_chunk$set(warning = FALSE,
                      message = FALSE,
                      echo = FALSE)
```


I am not a big NBA fan, to be honest I have started to follow it during the last season.
Luckily, one of the first matches I watched was a Grizzlies game and I had no option but keep appreciating Ja and his gang's show.
As I have already said, I am not a real NBA fan so I only watched Grizzlies games. For that reason, I am going to analyze him and other point guards in order to know if there is someone like him stats-wise.


### Dataset

```{r}
library(tidyverse)
library(kableExtra)

#Reading data and filtering to keep only PGs

nbaData = read_delim("2021-2022 NBA Player Stats - Regular.csv", delim=";", show_col_types = FALSE) %>% 
            filter(Pos == "PG")
```

The dataset used in this analysis is provided by "VIVO VINCO" on [Kaggle](https://www.kaggle.com/datasets/vivovinco/nba-player-stats). It brings a lot of attacking and defending stats of each player so as them age and the team he played for (if someone wear different jerseys along the season, there is an observation for each franchise and a total one as you can see below).

```{r}
kable(head(nbaData),caption = "First 5 lines of 2021-2022 NBA player stats dataset") %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"), font_size = 12) %>% 
  scroll_box(width = "900px")
```

```{r}
#selecting total stats from players who played for more than one team
tradedPlayers = nbaData %>%
                  group_by(Player) %>%
                  filter(n() > 1 & Tm == "TOT")

#Recombinig data so now it has only untraded players and total stats from those who were traded
nbaData = bind_rows(filter(group_by(nbaData, Player), n() == 1),
                    tradedPlayers)
                   
```


### Exploratory Data Analysis (EDA)
##Ja Morant
First of all, I want to see where Ja is located between other PGs in some stats and combination of them


## Related variables



## Creating new variables



### Principal Component Analysis (PCA)
